\vspace{-2cm}Formation Control of AAUSHIP

### 2015-11-14 paper.tex
Some more comments, and some fixmes added

@@

>>>>

Running the same setup as used in figure~\vref{fig:potform-po}, but with the addition of some objects in the way of the paths it can be seen how the ships tries to evade the obstacles. The obstacles potential field is drawn as black circles. It shall be noted the plotted boundary is not a hard boundary, but only shows the radius whereby the potential field of the obstacles can affect other objects.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/lawn-bar-formation-po}
  \caption{Same setups as in figure~\vref{fig:potform}, but with obstables positioned on the pathways.}
  \label{fig:potform-po}
\end{figure}
On the figure~\vref{fig:potform-po}, there are places two obstacles near each other on the first north going leg of the path. Here it is seen that two ships tries to gently diverge from the paths following near the boundry to the object, while it is seen that there is a ship going ``through'' the two objects. Because the two objects are offset a bit and about the same distance from the path it is seen that the ship avoids the center of the obstacles as much as possible.
\fixme{Dårlig formulering?}

@@

There is good room to improve the way the obstacles are generated, because the current setup with using point sources might not be an ideal way to represent obstacles in many situations. For example in the case of a pier, it will take quite a lot of point objects to represent such that no ships will try to ``squeeze through'' the pier, while it is a solid in reality.

\fixme{Kan vi diskutere og reflektere mere?}
